---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BridgeChange

`R` package `BridgeChange` constains functions useful to analyze time-series data 
and panel data with possibly large number of covariates and change-points.
This package offers a Bayesian inference on the linear regression mode under high-dimensinal covariates whose effects on the outcome are allowed to be heterogeneous across time.
This package will be useful to discover a set of predictive variables under dynamic setting where time-varying effect is expected to exist in many cases.

## Installation

You can install the most recent version of `BridgeChange` from Gitub using the [`devtools`](https://github.com/r-lib/devtools) package.

```{r}
# install BridgeChange from Github
# you might need to instal "devtools"
devtools::install_github("jongheepark/BridgeChange")
```



## Alvarez et al. data
```{r, warning=FALSE,echo=FALSE,message=FALSE}
# load packages 
library(BridgeChange)
library("pcse")
set.seed(1999)
data("agl")
data = agl
```



## Fit the one-way (time) fixed effect model using plm
The following two `model` arguments are availabel for the fixed-effects HMBB.
- the fixed effects model (`"within"`), the default,
- the pooling model (`"pooling"`),

We will use the one-way (time) fixed effect model because the original model has a time-invariant covariate (central).
```{r, message=FALSE,warning=FALSE}
model = "within"
index = c('country', 'year')
effect = 'time'
formula <- growth ~ lagg1 + opengdp + openex + openimp + leftc * central
pdata   <- pdata.frame(data, index)
pm <- plm(formula, data = pdata, model = model, effect = effect)
summary(pm)
```


## Inspect the model (response and residuals)
We take a look at the response data and panel residuals to check the sign of misfit due to time-varying effects. 
```{r}
## response
plot(pdata$growth)

## panel residuals
coplot(pm$residuals ~ pdata[,index[2]]|pdata[,index[1]], data=pdata, ## number=length(unique(pdata[,index[1]])),
       overlap=.1, col="brown", type="l", 
       panel = panel.smooth, xlab="panel residuals by group and time")
```

## Fitting HMBB
We fit three HMBBs with no break, one break, and two breaks to see whether effects of covariates change over time. To save time, we set mcmc = 100 here. `BridgeFixedPanel` transforms the panel data using `plm` arguments of `model`, `effect` and `index` first. Then, it fits HMBB on the transformed data. `n.break` sets the number of break to be estimated. 
```{r}
mcmc = 100; burn = 100; verbose = 100; thin = 1;
formula <- growth ~ lagg1 + opengdp + openex + openimp + leftc + central + inter
agl.cp0 <- BridgeFixedPanel(formula=formula, data = data, 
                            model = model, index = index, effect = effect,
                            mcmc=mcmc, verbose=verbose, Waic = TRUE, 
                            n.break = 0)
agl.cp1 <- BridgeFixedPanel(formula=formula, data = data, 
                            model = model, index = index, effect = effect,
                            mcmc=mcmc, verbose=verbose, Waic = TRUE, 
                            n.break = 1)
agl.cp2 <- BridgeFixedPanel(formula=formula, data = data, 
                            model = model, index = index, effect = effect,
                            mcmc=mcmc, verbose=verbose, Waic = TRUE, 
                            n.break = 2)
```

After fitting multiple models, we can compare their model-fits using WAIC. `WaicCompare` shows WAIC scores for a list of models. `plotWaic()` draws a plot of WAIC scores.
```{r}
## model selection by WAIC
waic <- WaicCompare(list(agl.cp0, agl.cp1, agl.cp2), print = TRUE)
plotWaic(waic)
```

In addition to WAIC, we compare transitions of hidden states. `plotState` in MCMCpack can be used to draw hidden state transitions. 
```{r}
## state changes
par(mfrow=c(1, 2))
plotState(agl.cp1, start=1970, legend.control =c(1970, 0.85), main="One break")
plotState(agl.cp2, start=1970, legend.control =c(1970, 0.85), main="Two breaks")
```

The one break model looks good. We check the time-varying movements of the one break model using `dotplotRegime()`. Colors in `dotplotRegime()` are determined by the size of coefficients in the first regime. Red means positive, blue means negative, and grey means close to 0 in the first regime.
```{r}
## all covariates
dotplotRegime(agl.cp1, hybrid=FALSE, start = 1970, location.bar=12, x.location="default",
              text.cex=0.8, main="Time-varying Movements of All Covariates")
## label as a legend
dotplotRegime(agl.cp1, hybrid=FALSE, start = 1970, location.bar=12, x.location="legend",
              text.cex=0.8, main="Time-varying Movements of All Covariates")
```

We visualize the movement of the selected covariate using `select` argument in `dotplotRegime()`. Here we choose the left-party government-related variable. 
```{r}
## leftc only
## select works like grep()
dotplotRegime(agl.cp1, hybrid=FALSE, start = 1970, location.bar=12, x.location="static",
              text.cex=0.8, select="left", main=("Left party-related covariates"))

```

