---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BridgeChange

`R` package `BridgeChange` constains functions useful to analyze time-series data 
and panel data with possibly large number of covariates and change-points.
This package offers a Bayesian inference on the linear regression mode under high-dimensinal covariates whose effects on the outcome are allowed to be heterogeneous across time.
This package will be useful to discover a set of predictive variables under dynamic setting where time-varying effect is expected to exist in many cases.


## Table of Contents

1. [Overview](#overview)
2. [Installation](#installation)
3. [Time-series Data](#time-series-data)



## Installation

You can install the most recent version of `BridgeChange` from Gitub using the [`devtools`](https://github.com/r-lib/devtools) package.

```r
# install BridgeChange from Github
# you might need to instal "devtools"
devtools::install_github("soichiroy/BridgeChange")
```



## Time-series Data

### Model

`BridgeChangeReg()` can be used to analyse time-series data with possible change-points.

The functions fits the linear model:
$$
y_{t} = \mathbf{X}^{\top}_{t}\beta_{s_{t}} + \epsilon_{s_{t}}
$$
where $s_{t} \in \{1, \ldots, M\}$ is an indicator of states.


```{r, warning=FALSE,echo=FALSE,message=FALSE}
# load packages 
require(BridgeChange)
```

### Example 

```{r, message=FALSE,warning=FALSE}
set.seed(1973);

##
## simulate dataset 
##

out <- BridgeChangeSim(ntime=100, predictor = 50, rho=0.2, constant.p = 0.5,
                       positive.jump=FALSE, varying.p = 0.2, break.point = 0.5, dgp.only=TRUE)

# plot simulated coefficients 
plot(1:length(out$true.beta[1,]), out$true.beta[1,], 
     xlab="predictor", ylab="coefficients", ylim=range(out$true.beta), type='n')
points(out$true.beta[1,], col="red", pch="1", cex=1)
points(out$true.beta[2,], col="blue", pch="2", cex=1)

# plot simulated data 
plot(lm(y ~ x, data = out)$resid, type = 'l', lwd = 1.3)
abline(v = 100/2, col = 'red', lty = 3, lwd = 1.5)
```

```{r}
##
## fit models 
##

# set mcmc parameters 
mcmc <- burn <- 500; thin <- 1; verbose <- 500

# fit no-break model
set.seed(11173)
out0 <- BridgeChangeReg(y=out$y, X=out$x, scale.data=TRUE, intercept=TRUE,
                        mcmc=mcmc, burn = burn, thin=thin, verbose=verbose,
                        alpha.MH=TRUE, n.break = 0, waic=TRUE)

# fit one-break model 
set.seed(11173)
out1 <- BridgeChangeReg(y=out$y, X=out$x, scale.data=TRUE,intercept=TRUE,
                        mcmc=mcmc, burn = burn, thin=thin, verbose=verbose,
                        alpha.MH=TRUE, n.break = 1, waic=TRUE)

# fit one-break model 
set.seed(11173)
out2 <- BridgeChangeReg(y=out$y, X=out$x, scale.data=TRUE,intercept=TRUE,
                        mcmc=mcmc, burn = burn, thin=thin, verbose=verbose,
                        alpha.MH=TRUE, n.break = 2, waic=TRUE)

```


```{r}
##
## Post-estimation 
##

# model selection by waic 
waic <- WaicCompare(list(out0, out1, out2), print = TRUE)


# state transition plot (provided by `MCMCpack`)
par(mfrow = c(1,2), mar = c(4, 2.5, 3.5, 1))
MCMCpack::plotState(out1)
MCMCpack::plotState(out2)
```


